---
output: github_document
---

---

## **qrismb**

---
<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

## qrismb : Quantile regression with induced smoothing approach and L1-minimization

The __qrismb__ package implements a regression modeling of the quantiles of residual life, remaining lifetime at a specific time. For estimation of regression parameters, we applies an induced smoothed version of the existing non-smooth estimating equations approaches, and also uses L1-minimization approach as well. For estimation of regression parameter, "smooth" method uses a robust sandwich-type covariance estimator of regression estimators with resampling method, and "nonsmooth" method uses full multiplier bootstrap approach. To handle data subject to right censoring, inverse probabilities of censoring are incorporated as weights. 

## Installation

You can install the development version from [GitHub](https://github.com/Kyuhyun07/qrismb) with:

``` {r github, eval = FALSE}
devtools::install_github("Kyuhyun07/qrismb")
library(qrismb)
```

## Example
Here are two examples.

```{r example}
## 1. Simulation data example
## Simulate survival data from quantile regression model with possible ascociated response
data.gen<-function(samplesize, censor){
  sim=matrix(NA,samplesize,5)
  colnames(sim) = c("T","C","Z","X","delta")
  colnames(sim) = c("T","C","Z","X","censored")
  # Generate C_i
  sim[,2] = runif(samplesize,0,censor)
  # Covariates (Control=0, Treatment=1)
  sim[,4] = rbinom(samplesize,size=1,p=0.5)
  # Generate T_i (Given Condition r=rho_0, k=2, exp(beta_0)=5, exp(beta_1)=2))
  unif = runif(n=samplesize ,min = 0,max = 1)
  for (q in 1:samplesize){
    if (sim[q,4]==0){
      sim[q,1]={{-log(1-unif[q])}^(1/k)}/r.initial.0
    } else {
      sim[q,1]={{-log(1-unif[q])}^(1/k)}/r.initial.1
    }
  }
  # Generate Y_i (min(T,C))
  sim[,3] = apply(sim[,1:2], 1, FUN=min)
  # Censoring indicator (Censored=0, Not censored=1)
  sim[,5]=I(sim[,1]<sim[,2])
  # Ordering
  sim = sim[order(sim[,3]),]
  n = nrow(sim)
  sim = as.data.frame(sim)
  return(sim)
}
## Necessary data for simulation data generation 
exp.beta.initial.0=5
exp.beta.initial.1=10
k=2
r.initial.0=(log(10/5))^(1/k)/exp.beta.initial.0
r.initial.1=(log(10/5))^(1/k)/exp.beta.initial.1
c.0=5000000
c.1=70.39
c.3=24.35
c.5=14.07
c.7=8.49
set.seed(2021)
a<-data.gen(200,c.3)

## Define parameters for qrismb
Z=a[,3]
nc=1
covariate=a[,4]
D=a[,5]
t_0=2
Q=0.5
ne=200

## Run qrismb
library(qrismb)
qrismb(a[,3], 1, a[,4], a[,5], 3, 0.5, 200, "rq", "smooth")
qrismb(a[,3], 1, a[,4], a[,5], 3, 0.5, 200, "one", "nonsmooth")
```

```{r example2, cache = TRUE}
## 2. real data example
## Load "retinopathy" data from R survival package
library(survival)
data("retinopathy")
## Pre-process the data
reti = retinopathy
reti_rev = reti
# covariate 1 : Risk group (rescale 6 to 12 -> 0.5 to 1)
reti_rev$risk = rescale(reti$risk, to=c(0,1), from=c(0,12))
# covariate 2 : Age (no change, continuous variable)
# covariate 3 : Type of Diabetes (adult = 1, juvenile = 0)
reti_rev$type = as.numeric(reti$type)-1
# covariate 4 : treatment (no change)
# covariate 5 : interaction (type x trt)
reti_rev$typextrt = reti_rev$type*reti$trt

## Define parameters for qrismb
Z=reti_rev$futime
nc=5
covariate=as.matrix(reti_rev[,c(9,4,5,6,10)])
D=reti_rev$status
t_0=1
Q=0.25
ne=200

## Run qrismb
qrismb(Z, nc, covariate, D, t_0, Q, ne, "rq", "smooth")
qrismb(Z, nc, covariate, D, t_0, Q, ne, "random", "nonsmooth")
```

## Reference 
Chiou, S., Kang, S., and Yan, J. (2014).  Fitting accelerated failure time model in routine survival analysis with R package aftgee. 
*Journal of Statistical Software*, **61**(11): 1--23. 

Li, R., Huang, X., & Cortes, J. (2016). Quantile residual life regression with longitudinal biomarker measurements for dynamic prediction. *Journal of the Royal Statistical Society*. **Series C** (Applied Statistics), 755-773.

Jung, S. H., Jeong, J. H., & Bandos, H. (2009). Regression on quantile residual life. *Biometrics*, **65**(4), 1203-1212.
