---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(comment = NA, prompt = TRUE, collapse = TRUE)
```
# qrismb

<!-- badges: start -->
<!-- badges: end -->

The __qrismb__ package implements a regression modeling of the quantiles of residual life, remaining lifetime at a specific time. For estimation of regression parameters, we applies an induced smoothed version of the existing non-smooth estimating equations approaches, and also uses L1-minimization approach as well. Furthermore, iterative procedure is implemented. For estimation of regression parameter, "smooth" method uses a robust sandwich-type covariance estimator of regression estimators with resampling method, and "nonsmooth" method uses full multiplier bootstrap approach. To handle data subject to right censoring, inverse probabilities of censoring are incorporated as weights. 


## Installation

You can install the released version of qrismb from [GitHub](https://github.com/Kyuhyun07/qrismb) with:

```{r github, eval = FALSE}
# install.packages("devtools")
devtools::install_github("Kyuhyun07/qrismb")
library(qrismb)
```
## Example

There are two examples

```{r example}
data.gen <- function(n) {
  r0 <- .2 * sqrt(log(2))
  r1 <- .1 * sqrt(log(2))
  dat <- data.frame(censoring = runif(n, 0, 24.35),
                    Time0 = sqrt(-log(1 - runif(n))),
                    X = rbinom(n, 1, .5))
  dat$Time0 <- ifelse(dat$X > 0, dat$Time0 / r1, dat$Time0 / r0)
  dat$Time <- pmin(dat$Time0, dat$censoring)
  dat$status <- 1 * (dat$Time0 < dat$censoring)
  subset(dat, select = c(Time, status, X))
}
set.seed(1)
dat <- data.gen(200)

library(qrismb)
fm <- Surv(Time, status) ~ X
fit1 <- qrismb(fm, data = dat, t0 = 1, Q = 0.5, ne = 200, "rq", "smooth")
fit2 <- qrismb(fm, data = dat, t0 = 1, Q = 0.5, ne = 200, "one", "nonsmooth")
fit3 <- qrismb(fm, data = dat, t0 = 1, Q = 0.5, ne = 200, "random", "iterative")

coef(fit1)
summary(fit2)
vcov(fit3)
```

```{r example2}
## 2. real data example
## Load "retinopathy" data from R survival package
library(survival)
## Real data application
data(cancer, package = "survival")
lung2 <- subset(lung, select = c(time, status, age, sex))
## tidy up the data
lung2$status <- lung2$status - 1
lung2$sex <- lung2$sex - 1

library(qrismb)
set.seed(1)
fm <- Surv(time, status) ~ age + sex
fit1 <- qrismb(fm, data = lung2, t0 = 0, Q = 0.5, ne = 200, "random", "smooth")
fit2 <- qrismb(fm, data = lung2, t0 = 30, Q = 0.5, ne = 200, "one", "nonsmooth")
fit3 <- qrismb(fm, data = lung2, t0 = 100, Q = 0.5, ne = 200, "rq", "iterative")

coef(fit1)
summary(fit2)
vcov(fit3)
```

## Reference 
Chiou, S., Kang, S., and Yan, J. (2014).  Fitting accelerated failure time model in routine survival analysis with R package aftgee. 
*Journal of Statistical Software*, **61**(11): 1--23. 

Li, R., Huang, X., & Cortes, J. (2016). Quantile residual life regression with longitudinal biomarker measurements for dynamic prediction. *Journal of the Royal Statistical Society*. **Series C** (Applied Statistics), 755-773.

Jung, S. H., Jeong, J. H., & Bandos, H. (2009). Regression on quantile residual life. *Biometrics*, **65**(4), 1203-1212.

